---
title: "Fish aggregation at ocean aquaculture can augment wild populations and local fishing"
subtitle: "Supplemental Information"
author: "Jessica L. Couture, Darcy Bradley, Benjamin S. Halpern, Steven D. Gaines"
output:
  pdf_document: default
  word_document: default
  html_document:
    code_folding: hide
    fig_width: 12
---


```{r warning=FALSE,message=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE)

library(tidyverse)
library(patchwork)
library(paletteer)
library(knitr)

```

This document includes the supplemental information for "Fish aggregation at ocean aquaculture can augment wild populations and local fisheries". 


## Figure S1

**Equilibrium biomass** relative to total biomass with no farm, for different levels of attraction to farms, fishery management, and varying total area coverage. For (A, C) one large contiguous farm and (B, D) total farm area broken up into smaller separate farms. Top plots (A, B) are run under strong fisheries management, bottom plots (C, D) are under poor management. Biomass difference is calculated as the difference between catch biomass with the farm scenario and a scenario with no farm.

```{r}
### Color palettes

### Attraction values
attrCols<-paletteer_d("beyonce::X19")[c(5,4,3,2)] # edit bc beyonce package doesn't work for this updated R version. Paletteer works th

names(attrCols)<-c(1,3,9,15)


### Farm size colors
# fsCols<-c(beyonce_palette(19)[5],beyonce_palette(22)[c(2,3,5)])#paletteer_d("ghibli::PonyoMedium")[c(1,3,6,4)]
fsCols<-c(paletteer_d("beyonce::X19")[5], paletteer_d("beyonce::X22")[c(2,3,5)])# edit bc beyonce package doesn't work for this updated R version. Paletteer works th
names(fsCols)<-c("20","10","5","2")


```

```{r}

msAttrOA<-read_csv("runs/openAccess/farmEq_msAttOALg.csv")
# msAttrOAs<-read_csv("runs/aqMS/farmEq_msAttrOASm.csv") # 2 farms at 10 patches each
msAttrOAxs<-read_csv("runs/openAccess/farmEq_msAttOAXSm.csv") # 4 farms at 5 patches each
nullOA<-read_csv("runs/openAccess/nullOA.csv")
# write_csv(nullOA,"runs/aqMS/nullOA.csv")

zerosBm<-data.frame(mpaSize=0,
                  attr=unique(msAttrOA$attr),
                  biomass=1,
                  catch=1,
                  diffBm=1,
                  diffCtch=1)

msAttrOA2<-msAttrOA%>%
  mutate(diffBm=biomass/as.numeric(nullOA[1,"biomass"]),
         diffCtch=catch/as.numeric(nullOA[1,"catch"]))%>%
  filter(mpaSize<0.5)%>%
  bind_rows(.,zerosBm)

# msAttrOAs2<-msAttrOAs%>%
#   mutate(diffBm=biomass-as.numeric(nullOA[1,"biomass"]),
#          diffCtch=catch-as.numeric(nullOA[1,"catch"]))

msAttrOAxs2<-msAttrOAxs%>%
  mutate(diffBm=biomass/as.numeric(nullOA[1,"biomass"]),
         diffCtch=catch/as.numeric(nullOA[1,"catch"]))%>%
  filter(mpaSize<0.5)%>%
  bind_rows(.,zerosBm)


##### Plots
sizeAttrBm<-ggplot(msAttrOA2,aes(x=mpaSize,y=diffBm*100,group=as.factor(attr),color=as.factor(attr)))+
  geom_hline(yintercept = 100,color="gray66")+
  geom_smooth(size=0.8,se=FALSE)+
  labs(title = "",y="% biomass",x="total farm area\n(% of total range)")+
  scale_y_continuous(limits = c(95,370))+
  scale_x_continuous(breaks = seq(0,0.4,by=0.1),labels = seq(0,0.4,by=0.1)*100)+
  scale_color_manual(values = attrCols, name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
    theme(axis.text=element_text(size=12),
          axis.title = element_text(size=16),
          legend.text = element_text(size=12),
        legend.title = element_text(size=16),
        plot.title = element_text(size=20))

sizeAttrBmS<-ggplot()+ ## replaced sm with xsm to excentuate differences (smaller farms)
  geom_hline(yintercept = 100,color="gray66")+
  geom_smooth(data=msAttrOAxs2,aes(x=mpaSize,y=diffBm*100,group=as.factor(attr),color=as.factor(attr)),size=0.8,se=FALSE)+
  labs(title = "",y="",x="total farm area\n(% of total range)")+
  scale_y_continuous(limits = c(95,370))+
  scale_x_continuous(breaks = seq(0,0.4,by=0.1),labels = seq(0,0.4,by=0.1)*100)+
  scale_color_manual(values = attrCols, name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
    theme(axis.text=element_text(size=12),
          axis.title = element_text(size=16),
          legend.text = element_text(size=12),
        legend.title = element_text(size=16),
        plot.title = element_text(size=20))

##### CE

msAttrCE<-read_csv("runs/constantEffortMSY/farmEq_msAttCELg.csv")

msAttrCExs<-read_csv("runs/constantEffortMSY/farmEq_msAttCEXsm.csv") # 4 farms at 5 patches each

nullCE<-read_csv("runs/constantEffortMSY/nullCEmsy.csv")

# nullCE<-read_csv("runs/aqMS/nullCE.csv")

msAttrCE2<-msAttrCE%>%
  mutate(diffBm=biomass/as.numeric(nullCE[1,"biomass"]),
         diffCtch=catch/as.numeric(nullCE[1,"catch"]))%>%
  filter(mpaSize<0.5)%>%
  bind_rows(.,zerosBm)

msAttrCExs2<-msAttrCExs%>%
  mutate(diffBm=biomass/as.numeric(nullCE[1,"biomass"]),
         diffCtch=catch/as.numeric(nullCE[1,"catch"]))%>%
  filter(mpaSize<0.5)%>%
  bind_rows(.,zerosBm)

### plot mpaSize by attraction

sizeAttrBmCE<-ggplot(msAttrCE2,aes(x=mpaSize,y=diffBm*100,group=as.factor(attr),color=as.factor(attr)))+
  geom_hline(yintercept = 100,color="gray66")+
  geom_smooth(size=0.8,se=FALSE)+
  #geom_point()+
  labs(title = "One large farm",y="% biomass",x="")+
  scale_y_continuous(limits = c(95,370))+
  scale_x_continuous(breaks = seq(0,0.4,by=0.1),labels = seq(0,0.4,by=0.1)*100)+
  scale_color_manual(values = attrCols,name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
    theme(axis.text=element_text(size=12),
          axis.title = element_text(size=16),
          legend.text = element_text(size=12),
        legend.title = element_text(size=16),
        plot.title = element_text(size=20))

sizeAttrBmSce<-ggplot()+ ## replaced sm with xsm to excentuate differences (smaller farms)
  geom_hline(yintercept = 100,color="gray66")+
  geom_smooth(data=msAttrCExs2,aes(x=mpaSize,y=diffBm*100,group=as.factor(attr),color=as.factor(attr)),size=0.8,se=FALSE)+
  labs(title = "Several smaller farms",y="",x="")+
  scale_y_continuous(limits = c(95,370))+
  scale_x_continuous(breaks = seq(0,0.4,by=0.1),labels = seq(0,0.4,by=0.1)*100)+
  scale_color_manual(values = attrCols,name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
    theme(axis.text=element_text(size=12),
          axis.title = element_text(size=16),
          legend.text = element_text(size=12),
        legend.title = element_text(size=16),
        plot.title = element_text(size=20))

figS1quadBm<-(sizeAttrBmCE+sizeAttrBmSce)/(sizeAttrBm +sizeAttrBmS)+
  plot_layout(guides = "collect")+
  plot_annotation(tag_levels = "A")&
    theme(plot.tag = element_text(face = 'bold'))

figS1quadBm

```

\newpage

## Figure S2

Farm impacts over time for a **high value open access fishery**. In each plot the level of attraction is varied. Top plots represent one large farm at 20% total coverage (A, B), and the bottom plots represent the 20% farm area broken into several smaller farms (C, D). Biomass and catches are in relative to the base scenario with no farm (farm scenario/no farm scenario).


```{r}

jattDat<-read_csv("runs/openAccess/timeJattOA_perc.csv")

##### Relative plots

attLg<-jattDat%>%
  filter(farmDesign=="large",
         year<101)

diffBmOAJAtt<-ggplot(attLg[attLg$year>49,],aes(year, bmDiff*100,color=as.factor(run))) +
  geom_hline(yintercept=100,color="gray66")+
  geom_line(size=0.75)+
  scale_y_continuous(expand=c(0,0),limits = c(100,255))+
  scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+   
  labs(x="Year",y="One large farm\n\n% Biomass",title="")+
  scale_color_manual(values = attrCols,name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))

diffCtchOAJAtt<-ggplot(attLg[attLg$year>49,],aes(year, ctchDiff*100,color=as.factor(run))) +
  geom_hline(yintercept=100,color="gray66")+  
  geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(60,130))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
    labs(x="year",y="% Catch",title = "")+
    scale_color_manual(values = attrCols,name="Attraction",labels=c("None","Low","Moderate","High"))+
    theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))

attSm<-jattDat%>%
  filter(farmDesign=="small",
         year<101)

diffBmOAJAttS<-ggplot(attSm[attSm$year>49,],aes(year, bmDiff*100,color=as.factor(run))) +
    geom_hline(yintercept=100,color="gray66")+
    geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(100,255))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
    labs(x="Year",y="Small farms\n\n% Biomass",title="")+
    scale_color_manual(values = attrCols,name="Attraction",labels=c("None","Low","Moderate","High"))+
    theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))

diffCtchOAJAttS<-ggplot(attSm[attSm$year>49,],aes(year, ctchDiff*100,color=as.factor(run))) +
  geom_hline(yintercept=100,color="gray66")+  
  geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(60,130))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
  labs(x="year",y="% Catch",title = "")+
  scale_color_manual(values = attrCols,name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))


((diffBmOAJAtt+diffCtchOAJAtt)/(diffBmOAJAttS+diffCtchOAJAttS))+
  plot_annotation(tag_levels = "A")+
  plot_layout(guides = "collect")

```

\newpage

## Figure S3

Farm impacts over time for a fishery fished at constant effort at maximum sustainable yield. In each plot the level of attraction is varied. Top plots represent one large farm at 20% total coverage (A, B), and the bottom plots represent the 20% farm area broken into several smaller farms (C, D). Biomass and catches are relative to the base scenario with no farm (farm scenario/no farm scenario).

```{r}

jattDatCE<-read_csv("runs/constantEffortMSY/timeJattCE_perc.csv")

##### Relative plots

attLgCE<-jattDatCE%>%
  filter(farmDesign=="large",
         year<101)

diffBmOAJAttCE<-ggplot(attLgCE[attLgCE$year>49,],aes(year, bmDiff*100,color=as.factor(run))) +
  geom_hline(yintercept=100,color="gray66")+
  geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(100,215))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
  labs(x="Year",y="One large farm\n\n% Biomass",title="")+
  scale_color_manual(values = attrCols, name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))

diffCtchOAJAttCE<-ggplot(attLgCE[attLgCE$year>49,],aes(year, ctchDiff*100,color=as.factor(run))) +
  geom_hline(yintercept=100,color="gray66")+  
  geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(55,110))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
    labs(x="year",y="% Catch",title = "")+
    scale_color_manual(values = attrCols, name="Attraction",labels=c("None","Low","Moderate","High"))+
    theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))

attSmCE<-jattDatCE%>%
  filter(farmDesign=="small",
         year<101)

diffBmOAJAttSCE<-ggplot(attSmCE[attSmCE$year>49,],aes(year, bmDiff*100,color=as.factor(run))) +
    geom_hline(yintercept=100,color="gray66")+
    geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(100,215))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
    labs(x="Year",y="Small farms\n\n% Biomass",title="")+
    scale_color_manual(values = attrCols, name="Attraction",labels=c("None","Low","Moderate","High"))+
    theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))

diffCtchOAJAttSCE<-ggplot(attSmCE[attSmCE$year>49,],aes(year, ctchDiff*100,color=as.factor(run))) +
  geom_hline(yintercept=100,color="gray66")+  
  geom_line(size=0.75)+
    scale_y_continuous(expand=c(0,0),limits = c(55,110))+
    scale_x_continuous(breaks=seq(50,100,by=10),labels=seq(0,50,by=10))+
  labs(x="year",y="% Catch",title = "")+
  scale_color_manual(values = attrCols, name="Attraction",labels=c("None","Low","Moderate","High"))+
  theme_bw()+
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size=14))


((diffBmOAJAttCE+diffCtchOAJAttCE)/(diffBmOAJAttSCE+diffCtchOAJAttSCE))+
  plot_annotation(tag_levels = "A")+
  plot_layout(guides = "collect")

```

\newpage


## Figure S4

Equilibrium differences in total biomass and catch biomass for different species based on adult movement for farm scenarios with very damaging effects on the wild population (damage > fishing mortality). Different farm designs are tested by farm size resulting in the indicated number of farms. 


```{r fig.height=3}

amFsOAnegKill<-read_csv("runs/openAccess/farmEq_amFsNegKill.csv")

amFsOAKill<-amFsOAnegKill%>%
  filter(farmSize>1)%>% 
  mutate(diffBm=biomass/as.numeric(nullOA[1,"biomass"]),
         diffCtch=catch/as.numeric(nullOA[1,"catch"]))

amFsBmKill<-ggplot(amFsOAKill,aes(x=adultMove,y=diffBm*100,group=as.factor(farmSize),color=as.factor(farmSize)))+
  geom_hline(yintercept = 100,color="gray66")+
  geom_smooth(size=0.8,se=FALSE)+
  scale_color_manual(values = fsCols,name="Number\nof farms", labels=20/c(2,5,10,20))+
  scale_y_continuous(limits = c(50,100))+
  labs(x="Adult movement",y="% Biomass")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=14))


amFsCtchKill<-ggplot(amFsOAKill,aes(x=adultMove,y=diffCtch*100,group=as.factor(farmSize),color=as.factor(farmSize)))+
 geom_hline(yintercept = 100,color="gray66")+
  geom_smooth(size=0.8,se=FALSE)+#geom_line(size=0.8)+
  scale_color_manual(values = fsCols,name="Number\nof farms", labels=20/c(2,5,10,20))+
  scale_y_continuous(limits = c(0,100))+
  labs(x="Adult movement",y="% Catch")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text = element_text(size = 12),
        axis.title = element_text(size=14))


amFsBmKill + amFsCtchKill + 
  plot_layout(guides = "collect")+
  plot_annotation(tag_levels = "A")
```

\newpage

## Figure S5

Relative differences in total biomass compared to no farm over a range of total farm areas. Farms are all divided into several smaller farms. Farm scenarios with positive (A, C) and negative impacts to the wild population (B, D), under strong (A, B) and weak (C, D) fishery management. 

```{r}

### Farm size colors:
# szCols<-c(beyonce_palette(129)[c(1,2,4)],beyonce_palette(6)[5])#paletteer_d("ghibli::PonyoMedium")[c(1,3,6,4)]

szCols<-c(paletteer_d("beyonce::X129")[c(1,2,4)], paletteer_d("beyonce::X6")[5])# edit bc beyonce package doesn't work for this updated R version. Paletteer works th
names(szCols)<-c("60","20","3","0")

szMgmtBen<-read_csv("runs/movement/farmEq_mpaMgmtAMBen.csv")

szMgmtBen2<-szMgmtBen%>%
  mutate(diffBm=case_when(mgmt == "oa" ~  biomass/as.numeric(nullOA[1,"biomass"]),
                          TRUE ~ biomass/as.numeric(nullCE[1,"biomass"])),
         diffCtch=case_when(mgmt=="oa" ~  catch/as.numeric(nullOA[1,"catch"]),
                          TRUE ~ catch/as.numeric(nullCE[1,"catch"])))

zeros<-data.frame(mpaSz=0,
                  aMove=rep(c(0,3,20,60),2),
                  mgmt=rep(c("oa","ce"),each=4),
                  diffBm=1,
                  diffCtch=1)

szMgmtBen3<-szMgmtBen2%>%
  bind_rows(.,zeros)%>%
  filter(mpaSz<0.5)


szMgmtBenBmOA<-ggplot(szMgmtBen3[szMgmtBen3$mgmt=="oa",],aes(x=mpaSz*100,y=diffBm*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(50,300))+
  labs(x="Total farm area",y="Weak mgmt\n\n% biomass",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


szMgmtBenBmCE<-ggplot(szMgmtBen3[szMgmtBen3$mgmt=="ce",],aes(x=mpaSz*100,y=diffBm*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(50,300))+
  labs(x="",y="Strong mgmt\n\n% biomass",title = "Positive impacts\n")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))

```

```{r}

szMgmtNeg<-read_csv("runs/movement/farmEq_mpaMgmtAMNeg.csv")

szMgmtNeg2<-szMgmtNeg%>%
  mutate(diffBm=case_when(mgmt == "oa" ~  biomass/as.numeric(nullOA[1,"biomass"]),
                          TRUE ~ biomass/as.numeric(nullCE[1,"biomass"])),
         diffCtch=case_when(mgmt=="oa" ~  catch/as.numeric(nullOA[1,"catch"]),
                          TRUE ~ catch/as.numeric(nullCE[1,"catch"])))

szMgmtNeg3<-szMgmtNeg2%>%
  bind_rows(.,zeros)


szMgmtNegBmOA<-ggplot(szMgmtNeg3[szMgmtNeg3$mgmt=="oa",],aes(x=mpaSz*100,y=diffBm*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  #geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(50,300))+
  labs(x="Total farm area",y="",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


szMgmtNegBmCE<-ggplot(szMgmtNeg3[szMgmtNeg3$mgmt=="ce",],aes(x=mpaSz*100,y=diffBm*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  #geom_smooth(size=0.8,se=FALSE)+
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(50,300))+
  labs(x="",y="",title = "Negative impacts\n")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))

figS5Plts<-((szMgmtBenBmCE + szMgmtNegBmCE)/(szMgmtBenBmOA + szMgmtNegBmOA )) +
  plot_annotation(tag_levels = 'A') + 
  plot_layout(guides="collect")


figS5Plts

```

\newpage

## Figure S6

Relative differences in total biomass and catches compared to no farm over a range of total farm areas. Farms are all divided into several smaller farms. Here farms have no impact on wild population natural mortality rates.


```{r}

szMgmt0<-read_csv("runs/movement/farmEq_mpaMgmtAM0.csv")

szMgmt02<-szMgmt0%>%
  mutate(diffBm=case_when(mgmt == "oa" ~  biomass/as.numeric(nullOA[1,"biomass"]),
                          TRUE ~ biomass/as.numeric(nullCE[1,"biomass"])),
         diffCtch=case_when(mgmt=="oa" ~  catch/as.numeric(nullOA[1,"catch"]),
                          TRUE ~ catch/as.numeric(nullCE[1,"catch"])))

szMgmt03<-szMgmt02%>%
  bind_rows(.,zeros)%>%
  filter(mpaSz<0.5)

# open access

szMgmt0BmOA<-ggplot(szMgmt03[szMgmt03$mgmt=="oa",],aes(x=mpaSz*100,y=diffBm*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(95,250))+
  labs(x="Total farm area",y="weak mgmt\n\n% biomass",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


szMgmt0CtchOA<-ggplot(szMgmt03[szMgmt03$mgmt=="oa",],aes(x=mpaSz*100,y=diffCtch*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(50,140))+
  labs(x="Total farm area",y="% catch",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))

# effort @ MSY

szMgmt0BmCE<-ggplot(szMgmt03[szMgmt03$mgmt=="ce",],aes(x=mpaSz*100,y=diffBm*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(95,250))+
  labs(x="",y="Strong mgmt\n\n% biomass",title = "Biomass")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


szMgmt0CtchCE<-ggplot(szMgmt03[szMgmt03$mgmt=="ce",],aes(x=mpaSz*100,y=diffCtch*100,group=aMove,color=as.factor(aMove)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_manual(values = rev(szCols),name="Adult\nmovement",labels=c("None","Low","Moderate","High"))+
  scale_y_continuous(limits = c(50,140))+
  labs(x="",y="% catch",title = "Catch")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))

figS6Plts<-((szMgmt0BmCE + szMgmt0CtchCE)/(szMgmt0BmOA + szMgmt0CtchOA )) +
  plot_annotation(tag_levels = 'A') + 
  plot_layout(guides="collect")


figS6Plts

```

\newpage

## Figure S7

Relative differences in total biomass (A, C) and catches (B, D) under strong (A, B) and weak (C, D) fishery management compared to no farm over a range of total farm areas. Farms are all divided into several smaller farms. Here farms have varying impacts on wild population natural mortality rates (0-20% negative impacts).


```{r}

szMgmtDMG<-read_csv("runs/movement/farmEq_mpaMgmtDmg.csv")

szMgmtDMG2<-szMgmtDMG%>%
  mutate(diffBm=case_when(mgmt == "oa" ~  biomass/as.numeric(nullOA[1,"biomass"]),
                          TRUE ~ biomass/as.numeric(nullCE[1,"biomass"])))

szMgmtDMG3<-szMgmtDMG2%>%
  bind_rows(.,data.frame(mpaSz=0,
                         damage=rep(c(1,1.05,1.1,1.15,1.2),2),
                         mgmt=c(rep("oa",5),rep("ce",5)),
                         biomass=NA,
                         catch=NA,
                         diffBm=1.0,
                         ctchDiff=1.0))

# open access

szMgmtDmgBmOA<-ggplot(szMgmtDMG3[szMgmtDMG3$mgmt=="oa",],aes(x=mpaSz*100,y=diffBm*100,group=damage,color=as.factor(damage)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_viridis_d(name="Negative\nImpact",labels=c("0","5%","10%","15%","20%"),direction = -1)+
  scale_y_continuous(limits = c(70,250))+
  labs(x="Total farm area",y="Weak mgmt\n\n% biomass",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


szMgmtDmgCtchOA<-ggplot(szMgmtDMG3[szMgmtDMG3$mgmt=="oa",],aes(x=mpaSz*100,y=ctchDiff*100,group=damage,color=as.factor(damage)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_viridis_d(name="Negative\nImpact",labels=c("0","5%","10%","15%","20%"),direction = -1)+
  scale_y_continuous(limits = c(70,250))+
  labs(x="Total farm area",y="Weak mgmt\n\n% catch",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))

### Constant effort

szMgmtDmgBmCE<-ggplot(szMgmtDMG3[szMgmtDMG3$mgmt=="ce",],aes(x=mpaSz*100,y=diffBm*100,group=damage,color=as.factor(damage)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_viridis_d(name="Negative\nImpact",labels=c("0","5%","10%","15%","20%"),direction = -1)+
  scale_y_continuous(limits = c(70,250))+
  labs(x="Total farm area",y="Strong mgmt\n\n% biomass",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


szMgmtDmgCtchCE<-ggplot(szMgmtDMG3[szMgmtDMG3$mgmt=="ce",],aes(x=mpaSz*100,y=ctchDiff*100,group=damage,color=as.factor(damage)))+
  geom_hline(yintercept = 100,color="gray66")+
  # geom_smooth(size=0.8,se=FALSE)+#
  geom_line(size=0.8)+
  scale_color_viridis_d(name="Negative\nImpact",labels=c("0","5%","10%","15%","20%"),direction = -1)+
  scale_y_continuous(limits = c(70,250))+
  labs(x="Total farm area",y="Strong mgmt\n\n% catch",title = "")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5, size = 16),
        axis.text=element_text(size=12),
        axis.title = element_text(size=16),
        legend.text = element_text(size=12),
        legend.title = element_text(size=16))


figS7Plts<-((szMgmtDmgBmCE + szMgmtDmgCtchCE)/(szMgmtDmgBmOA + szMgmtDmgCtchOA )) +
  plot_annotation(tag_levels = 'A') + 
  plot_layout(guides="collect")

figS7Plts

```